Synthesis report

### 2020-02-19 analysis/reports/synthesis.Rmd
cdf exploring

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples))
```

@@

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_d()

@@

```{r size of fs}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
  geom_point(alpha = .3) +
  theme_bw() +
  scale_color_viridis_c(option = "magma", end = .9)

@@

```{r nparts vs avgn}
ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = log_nparts, color = log(s0))) +
  theme_bw() +
  geom_point(alpha = .2) +
  scale_color_viridis_c()

@@

```{r nsamples}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
  geom_point(alpha = .3) +
  theme_bw() +
  scale_color_viridis_c(option = "magma", end = .9)

ggplot(filter(all_di, singletons == F, nsamples <  max(nsamples)), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "magma", end = .9)
```

@@

The vertical lines are the 10% and 95% marks, from left to right. When we got relatively few samples (`r min(all_di$nsamples)`), we had found `r exp(filter(all_di, nsamples == min(nsamples))$log_nsamples -  filter(all_di, nsamples == min(nsamples))$log_nparts)` of that feasible set. And there's a clear negative relationship between the proportion of the FS that we've found and the number of samples we got, once we start getting about 10% of the feasible set. This makes sense; at that point we have a 1 in 10 chance of drawing one we've already seen. But for almost all cases, we're sampling only a miniscule proportion of the feasible set - median of `r median(exp(all_di$log_nsamples - all_di$log_nparts))`! - and get no duplicates.

@@

#

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts))
```

@@

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .2) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_d()

@@

```{r size of fs}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
  geom_point(alpha = .3) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)

@@

```{r nparts vs avgn}
ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = log_nparts, color = log(s0))) +
  theme_bw() +
  geom_point(alpha = .2) +
  theme(legend.position = "top") + scale_color_viridis_c()

@@

```{r nsamples}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
  geom_point(alpha = .3) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)

ggplot(filter(all_di, singletons == F, nsamples <  max(nsamples)), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)
```

@@

The vertical lines are the 10% and 95% marks, from left to right. When we got relatively few samples (`r min(filter(all_di, singletons == F, nsamples > 1)$nsamples)`), we had found `r 100 * exp(filter(all_di, nsamples == min(filter(all_di, singletons == F, nsamples > 1)$nsamples))$log_nsamples[1] -  filter(all_di, nsamples == min(filter(all_di, singletons == F, nsamples > 1)$nsamples))$log_nparts[1])`% of that feasible set. And there's a clear negative relationship between the proportion of the FS that we've found and the number of samples we got, once we start getting about 10% of the feasible set. This makes sense; at that point we have a 1 in 10 chance of drawing one we've already seen. But for almost all cases, we're sampling only a miniscule proportion of the feasible set - median of `r median(exp(all_di$log_nsamples - all_di$log_nparts))`! - and get no duplicates.

@@

# Distribution of percentile values

## Skewness
```{r skew percentiles}
ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = skew_percentile, color = prop_found)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
  theme(legend.position = "top")

all_di$many_found <- all_di$prop_found >= .5

ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(many_found))

ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = skew_percentile, color = log(s0))) +
  geom_point(alpha = .2) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c()
```

## Simpson
```{r simpson percentiles}
ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = simpson_percentile, color = prop_found)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
  theme(legend.position = "top")

ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(many_found))

ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = simpson_percentile, color = log(s0))) +
  geom_point(alpha = .2) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c()
```

Do S and N predict percentile?
